Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-22 ICML-submission/empirical-comparison.tex
small fix

We generate strongly and weakly separable samples with $K=3$ in a similar sense those in Figure~\ref{figure:weakly-linearly-separable-examples-with-margin}. They are originally generated in a $d=2$ plate, and then lifted to $d=3$ by adding a constant feature. We provide the figures of their exact look in Appendix~\ref{sec:supp-to-experiment}. Different from Figure~\ref{figure:weakly-linearly-separable-examples-with-margin}, the three classes are non-uniform and imbanlanced: class 1 occupies a smaller sector between $-15^\circ$ and $15^\circ$, while class 2 and class 3 occupy $[15^\circ, 180^\circ]$ and $[-180^\circ, -15^\circ]$ respectively. On the other hand, $80\%$ of data comes from class 1, while $10\%$ comes from class 2 and 3 each.

>>>>

We generate strongly and weakly separable samples with $K=3$ in a similar sense to those in Figure~\ref{figure:weakly-linearly-separable-examples-with-margin}. They are originally generated in a $d=2$ plate, and then lifted to $d=3$ by adding a constant feature. We provide the figures of their exact look in Appendix~\ref{sec:supp-to-experiment}. Different from Figure~\ref{figure:weakly-linearly-separable-examples-with-margin}, the three classes are non-uniform and imbanlanced: class 1 occupies a smaller sector between $-15^\circ$ and $15^\circ$, while class 2 and class 3 occupy $[15^\circ, 180^\circ]$ and $[-180^\circ, -15^\circ]$ respectively. On the other hand, $80\%$ of data comes from class 1, while $10\%$ comes from class 2 and 3 each.
